\documentclass{article}

\usepackage{amsmath, amsfonts, geometry}

\begin{document}

\section*{Discussion}
I picked a selection of 10 problems from Silverman and Washington which I felt were the most relevant problems to my project. Washington provides a section on cryptography but only a single question about Diffie-Hellman (with many questions about outdated El-Gamal), which left me with a lack of questions related to cryptographic applications. Hopefully the coding aspect substitutes for that to some extent.

Some of these questions are a bit long, so I'm not sure if I should complete them all (thoughts?).

My thoughts on the order of completing the problems (grouped by most to least relevant):
\begin{itemize}
\item Silverman 1.2, 1.11, 1.12, 1.19
\item Silverman 1.17, 1.18; Washington 2.5
\item Silverman 1.14; Washington 2.17, 6.1
\end{itemize}

\section{Silverman 1.2}
Let $C$ be the conic given by the equation
$$F(x,y) = ax^2 + bxy + cy^2 + dx + ey + f = 0$$
and let $\delta$ be the determinant
$$\det \begin{bmatrix}
2a & b & d \\
b & 2c & e \\
d & e & 2f \\
\end{bmatrix}$$

(a) Show that if $\delta \neq 0$ then $C$ has no singular points. That is, show there are no points $(x,y)$ where
$$F(x,y) = \frac{\partial F}{\partial x}(x,y) = \frac{\partial F}{\partial y}(x,y) = 0$$

In homogenous form we have:
$$\bar F = ax^2 + bxy + cy^2 + dxz + eyz + fz^2$$
$$\frac{\partial \bar F}{\partial x} = 2ax + by + dz$$
$$\frac{\partial \bar F}{\partial y} = bx + 2cy + ez$$
$$\frac{\partial \bar F}{\partial z} = dx + ey + 2fz$$

$\delta \neq 0$ implies that the our matrix is invertible, i.e. that the only solution to $Ax = 0$ is $x = 0$. But there is no point $(0,0,0)$ in projective space. So $C$ has no singular points.

(b) Conversely, show that if $\delta = 0$ and $b^2 - 4ac \neq 0$ then there is a unique singular point on $C$.

If we have a degenerate conic ($\delta = 0$) then we can classify it on whether $J = b^2 - 4ac$ is greater, equal, or less than zero. If $b^2-4ac < 0$, then the conic is two intersecting lines, and has one singular point (the point of intersection). If $b^2 - 4ac > 0$ then the conic is a single singular point. See Dennis, \textit{A Catalog of Special Plane Curves} for a reference.

(c) Let $L$ be the line $y = \alpha x + \beta$ with $\alpha \neq 0$. Show that the intersection of $L$ and $C$ consists of either zero, one, or two points.

Substitute the equation of the line into the equation for the conic.

\begin{align*}
0 &= ax^2 + bx(\alpha x + \beta) + c(\alpha x + \beta)^2 + dx + e(\alpha x + \beta) + f \\
&= ax^2 + \alpha b x^2 + \beta b x + \alpha^2 c x^2 + 2\alpha\beta c x + c\beta^2 + dx + \alpha e x + \beta e + f \\
&= (a + \alpha b + \alpha^2 c)x^2 + (\beta b + 2\alpha\beta c + d + \alpha e)x + (c\beta^2 + \beta e + f) \\
&= a'x^2 + b'x + c'
\end{align*}

In $\mathbb{R}$, this quadratic equation has zero, one, or two solutions depending on its coefficients.

(d) Determine the conditions on the coefficients which ensure that the intersection $L \cap C$ consists of exactly one point. What is the geometric significance of these conditions?

There is exactly one solution if $b'^2 - 4a'c' = 0$. In geometric terms, this line must be tangent to the curve.

\section{Silverman 1.11}
Let $S$ be a set with a composition law $*$ satisfying the following two properties:

(i) $P*Q = Q*P$ for all $P,Q \in S$

(ii) $P*(P*Q) = Q$ for all $P,Q \in S$

Fix an element $\mathcal{O} \in S$, and define a new composition law $+$ by the rule $P+Q = \mathcal{O} * (P * Q)$

(a) Prove that $+$ is commutative and has $\mathcal{O}$ as identity element.

Let $P,Q \in S$. Then $P+Q = \mathcal{O} * (P * Q) = \mathcal{O} * (Q * P) = Q+P$ so $+$ is commutative.

$P + \mathcal{O} = \mathcal{O} * (P * \mathcal{O}) = \mathcal{O} * (\mathcal{O} * P) = P$ so $\mathcal{O}$ is the identity.

(b) Prove that for any given $P,Q \in S$, the equation $X+P = Q$ has the unique solution $X = P*(Q*\mathcal{O})$ in $S$. In particular, if we define $-P$ to be $P*(\mathcal{O} * \mathcal{O})$ then $-P$ is the unique solution in $S$ of the equation $X+P = \mathcal{O}$.

Let $J, K, L \in S$. We have cancellation for $*$ as follows:

\begin{align*}
J * K &= J * L\\
J * (J * K) &= J * (J * L)\\
K &= L
\end{align*}

and cancellation works on both sides because $*$ commutes. Then

\begin{align*}
X+P & = Q \\
& = \mathcal{O} * (\mathcal{O} * Q) \\
\mathcal{O} * (X * P) &= \mathcal{O} * (\mathcal{O} * Q) \\
X * P &= \mathcal{O} * Q \\
&= Q * \mathcal{O} \\
&= P * (P * (Q * \mathcal{O})) \\
&= (P * (Q * \mathcal{O})) * P \\
X &= (P * (Q * \mathcal{O}))
\end{align*}.

Finally

\begin{align*}
X+P &= \mathcal{O}\\
X &= (P * (\mathcal{O} * \mathcal{O}))\\
X &= -P
\end{align*}.

(c) Prove that $+$ is associative (and so $(S,+)$ is a group) if and only if:

(iii) $R*(\mathcal{O}*(P*Q)) = P*(\mathcal{O}*(Q*R))$ for all $P,Q,R \in S$

($\Leftarrow$) Let $P,Q,R \in S$ and assume (iii).

\begin{align*}
P + (Q + R) &= P + (\mathcal{O} * (Q * R)) \\
&= \mathcal{O} * (P * (\mathcal{O} * (Q * R))) \\
&= \mathcal{O} * (R * (\mathcal{O} * (P * Q))) \\
&= R + (\mathcal{O} * (P * Q)) \\
&= R + (P + Q) \\
&= (P + Q) + R
\end{align*}

($\Rightarrow$) Let $P,Q,R \in S$ and assume $+$ is commutative.

\begin{align*}
P + (Q + R) &= (P + Q) + R \\
&= R + (P + Q) \\
\mathcal{O} * (P * (\mathcal{O} * (Q * R))) &= \mathcal{O} * ( R * (\mathcal{O} * (P * Q))) \\
P * (\mathcal{O} * (Q * R)) &= R * (\mathcal{O} * (P * Q))
\end{align*}

(d) Let $\mathcal{O}' \in S$ be another point, and define a composition law $+'$ by $P +' Q = \mathcal{O}' * (P*Q)$. Suppose that both $+$ and $+'$ are associative, so we obtain two group structures $(S,+)$ and $(S,+')$ on $S$. Prove that the map $\phi: P \mapsto \mathcal{O}*(\mathcal{O}'*P)$ is a group isomorphism from $(S,+)$ to $(S,+')$.

\begin{align*}
\phi(P+Q) &= \mathcal{O} * (\mathcal{O}' * (P + Q)) \\
&= \mathcal{O}' + (P+Q) \\
&= (\mathcal{O}'+P)+Q \\
&= ((\mathcal{O}' +' \mathcal{O}')+P)+Q \\
&= (\mathcal{O}' +' (\mathcal{O}'+P))+Q \\
&= ((\mathcal{O}'+P) +' \mathcal{O}')) + Q \\
&= (\mathcal{O}'+P) +' (\mathcal{O}' + Q) \\
&= \phi(P) +' \phi(Q)
\end{align*}
So $\phi$ is a group homomorphism from $(S,+)$ to $(S,+')$.

Let $\phi(P) = \mathcal{O}'$ for some $P \in S$.
\begin{align*}
\mathcal{O}' &= \phi(P) \\
\mathcal{O}' &= \mathcal{O}' + P \\
\mathcal{O}' + \mathcal{O} &= \mathcal{O}' + P \\
\mathcal{O} &= P
\end{align*}
So $\ker\phi = \{\mathcal{O}\}$, and thus $\phi$ is an isomorphism.

(e) Find a set $S$ with a composition law $*$ satisfying (i) and (ii) such that $(S,+)$ is not a group.

\section{Silverman 1.12}
The cubic curve $u^3 + v^3 = \alpha$ (with $\alpha \neq 0$) has a rational point $[1,-1,0]$ at infinity. Taking this rational point to be $\mathcal{O}$, we can make the points on the curve into a group.

(a) Derive a formula for the sum $P_1 + P_2$ of two points $P_1 = (u_1, v_1)$ and $P_2 = (u_2, v_2)$.

Line between $P_1$ and $P_2$:
$$m = \frac{v_2 - v_1}{u_2 - u_1}$$
$$b = v_1 - mu_1$$
$$v = mu + b$$

Substitute:
$$u^3 + (mu + b)^3 = \alpha$$
$$u^3 + b^3 + 3b^2mu + 3bm^2u^2 + m^3u^3 - \alpha = 0$$
$$(1+m^3) u^3 + 3bm^2 u^2 + 3b^2m u + b^3 - \alpha = 0$$
$$u^3 + \frac{3bm^2}{1+m^3}u^2 + \frac{3b^2m}{1+m^3}u + \frac{b^3-\alpha}{1+m^3} = 0$$

We know two roots:
$$(u-u_1)(u-u_2)(u-u_3) = 0$$

Coefficient of $u^2$ is $-u_1-u_2-u_3$, so:
$$u_1 + u_2 + u_3 = -\frac{3bm^2}{1+m^3}$$

Thus we have solved for the third point $(u_3,v_3)$:
$$u_3 = - u_1 - u_2 - \frac{3bm^2}{1+m^3}$$
$$v_3 = mu_3 + b$$

The third point $P_3 = P_1 + P_2$ then has the coordinates $P_3 = (u_3, -v_3)$.

(b) Derive a duplication formula for $2P$ in terms of $P = (u,v)$.

We have by implicit differentation that:
$$3u^2 - 3v^2 \frac{dv}{du} = 0$$
$$m = \frac{dv}{du} = -\frac{u^2}{v^2}$$

Then we can use the above formula with this slope to find the new point.

\section{Silverman 1.14}
Let $C$ be the cubic curve $u^3 + v^3 = u+v+1$. In the projective plane this curve has a point $[1,-1,0]$ at infinity. Find rational functions $x = x(u,v)$ and $y=y(u,v)$ so that $x$ and $y$ satisfy a cubic equation in Weierstrass normal form with the given point still at infinity.

\section{Silverman 1.17}
Let $C$ be a cubic curve in the projective plane given by the homogenous equation 
$$Y^2 Z = X^3 + aX^2 Z + bXZ^2 + cZ^3$$
Verify that the point $[0,1,0]$ at infinity is a non-singular point of $C$.

Let $\hat F = X^3 + aX^2 Z + bXZ^2 + cZ^3 - Y^2Z$. We have the following partial derivatives:
\begin{align*}
\frac{\partial \bar F}{\partial x} &= 3Z^2 + 2aZX + bZ^2 \\
\frac{\partial \bar F}{\partial y} &= 2ZY \\
\frac{\partial \bar F}{\partial z} &= 3cZ^2 + 2bXZ + aX^2 - Y^2
\end{align*}

Evaluating at the point $[0,1,0]$ we find that
\begin{align*}
\frac{\partial \bar F}{\partial x} &= 0 \\
\frac{\partial \bar F}{\partial y} &= 0 \\
\frac{\partial \bar F}{\partial z} &= -1
\end{align*}

So $\frac{\partial \hat F}{\partial z} \neq 0$ and thus $[0,1,0]$ is non-singular.

\section{Silverman 1.18}
The cubic curve $y^2 = x^3 + 17$ has the following five rational points:
$$P_1 = (-2,3), P_2 = (-1,4), P_3 = (2,5), P_4 = (4,9), P_5 = (8,23)$$

(a) Show that $P_2$, $P_4$, and $P_5$ can each be expressed as $mP_1 + nP_3$ for an appropriate choice of integers $m$ and $n$.

Initially I wrote code to solve this problem. Then I realized that I needed to represent rational numbers exactly, and decided it would be simpler to do something else.

Using the Pari/GP software I found the following:
\begin{verbatim}
? e1=ellinit([0,0,0,0,17])
? {
for(m = -5, 5,
  for(n = -5, 5,
    print(m); print(n);
    print(elladd(e1, ellmul(e1, [-2,3], m), ellmul(e1, [2,5], n)))
  )
)
}
\end{verbatim}

\begin{align*}
P_2 &= -2P_1 + P_2 \\
P_4 &= P_1 + -P_2 \\
P_5 &= -2P_1 + 0P_2
\end{align*}

(b) Compute the points $P_6 = -P_1 + 2P_3$ and $P_7 = 3P_1 - P_3$.
\begin{verbatim}
? elladd(e1, ellmul(e1, [-2,3], -1), ellmul(e1, [2,5], 2))
%6 = [43, 282]
? elladd(e1, ellmul(e1, [-2,3], 3), ellmul(e1, [2,5], -1))
%7 = [52, 375]
\end{verbatim}

(c) Notice that the points $P_1$ to $P_7$ all have integer coordinates. There is exactly one more rational point on this curve which has integer coordinates and $y > 0$. Find that point.

From (a), I have the point $-4P_1 + 3P_3 = (5234, 378661)$.

\section{Silverman 1.19}
Suppose that $P = (x,y)$ is a point on the cubic curve
$$y^2 = x^3 + ax^2 + bx + c$$

(a) Verify that the $x$ coordinate of the point $2P$ is given by the duplication formula
$$x(2P) = \frac{x^4 - 2bx^2 - 8cx - 4ac + b^2}{4y^2}$$

\begin{align*}
x(2P) &= \lambda^2 - a - 2x \\
\lambda &= \frac{3x^2 + 2ax + b}{2y} \\
x(2P) &= (\frac{3x^2 + 2ax + b}{2y})^2 - a - 2x \\
x(2P) &= \frac{9x^4 + 12ax^3 + (4a^2 + 6b)x^2 + 4abx + b^2}{4y^2} - a - 2x \\
x(2P) &= \frac{9x^4 + 12ax^3 + (4a^2 + 6b)x^2 + 4abx + b^2}{4y^2} - a\frac{4y^2}{4y^2} - 2x\frac{4y^2}{4y^2} \\
x(2P) &= \frac{9x^4 + 12ax^3 + (4a^2 + 6b)x^2 + 4abx + b^2 - 4ay^2 - 8xy^2}{4y^2}
\end{align*}

\begin{align*}
4ay^2 &= 4a(x^3 + ax^2 + bx + c) \\
&= 4ax^3 + 4a^2x^2 + 4abx + 4ac \\
8xy^2 &= 8x(x^3 + ax^2 + bx + c) \\
&= 8x^4 + 8ax^3 + 8bx^2 + 8cx
\end{align*}

\begin{align*}
& 9x^4 + 12ax^3 + (4a^2 + 6b)x^2 + 4abx + b^2 - 4ay^2 - 8xy^2\\
=~& 9x^4 + 12ax^3 + (4a^2 + 6b)x^2 + 4abx + b^2 - (4ax^3 + 4a^2x^2 + 4abx + 4ac) - (8x^4 + 8ax^3 + 8bx^2 + 8cx) \\
=~& (9x^4 - 8x^4) + (12ax^3 - 4ax^3 - 8ax^3) + (4a^2x^2 + 6bx^2 - 4a^2x^2 - 8bx^2) + (4abx - 4abx - 8cx) + (b^2 - 4ac) \\
=~& x^4 - 2bx^2 - 8cx + b^2 - 4ac
\end{align*}

Thus
$$x(2P) = \frac{x^4 - 2bx^2 - 8cx - 4ac + b^2}{4y^2}$$

(b) Derive the formula for the $y$ coordinate of $2P$ in terms of $x$ and $y$.
$$v = y - \lambda x$$

\begin{align*}
y(2P) &= \lambda x(2P) + v \\
&= \frac{3x^2 + 2ax + b}{2y}\frac{x^4 - 2bx^2 - 8cx - 4ac + b^2}{4y^2} + y - \lambda x \\
&= \frac{(3x^2 + 2ax + b)(x^4 - 2bx^2 - 8cx - 4ac + b^2)}{8y^3} + y - \frac{3x^3 + 2ax^2 + bx}{2y}
\end{align*}

(c) Find a polynomial in $x$ whose roots are the $x$ coordinates of the points $P=(x,y)$ satisfying $3P=\mathcal{O}$. (Hint: the relation $3P = \mathcal{O}$ can be written $2P = -P$.)

\begin{align*}
\frac{x^4 - 2bx^2 - 8cx - 4ac + b^2}{4y^2} &= x \\
x^4 - 2bx^2 - 8cx - 4ac + b^2 &= 4xy^2 \\
&= 4x(x^3 + ax^2 + bx + c) \\
&= 4x^4 + 4ax^3 + 4bx^2 + 4cx \\
0 &= 4x^4 - x^4 + 4ax^3 + 4bx^2 + 2bx^2 + 4cx + 8cx + 8ac - b^2 \\
0 &= 3x^4 + 4ax^3 + 6bx^2 + 12cx + 8ac - b^2
\end{align*}

(d) For the curve $y^2 = x^3 + 1$, solve the equation in (c) to find all of the points satisfying $3P = \mathcal{O}$.

We have $a = 0$, $b = 0$, and $c = 1$. We can thus simplify our equation:
\begin{align*}
0 &= 3x^4 + 4ax^3 + 6bx^2 + 12cx + 8ac - b^2 \\
&= 3x^4 + 12x \\
&= 3x(x^3 + 4)
\end{align*}

Which has zeroes at $x = 0,-2^\frac{2}{3},-i(2^\frac{2}{3}),-(i^\frac{1}{3})(2^\frac{2}{3})$. These correspond to the points:
$$(0, 0),~\left(-2^\frac{2}{3}, \pm \sqrt{-2^\frac{2}{3} + 1}\right),$$
$$\left(-i(2^\frac{2}{3}), \pm \sqrt{-i(2^\frac{2}{3}) + 1}\right),~\left(-(i^\frac{1}{3}(2^\frac{2}{3}), \pm \sqrt{-(i^\frac{1}{3})(2^\frac{2}{3}) + 1}\right)$$

\section{Washington 2.5}
Let $(x,y)$ be a point on the elliptic curve $E$ given by $y^2 = x^3 + Ax + B$. Show that if $y = 0$ then $3x^2 + A \neq 0$. 

If $y = 0$ then $(x,y)$ on $E$ satisfies the following condition:
$$0 = x^3 + Ax + B$$

However, the point must be nonsingular. $\frac{\partial F}{\partial y} = 0$, so $\frac{\partial F}{\partial x}$ must be nonzero, or the point is singular. Thus
$$\frac{\partial F}{\partial x} = 3x^2 + A \neq 0$$

\section{Washington 2.17}
(a) Show that $(x,y) \mapsto (x, -y)$ is a group homomorphism from E to itself, for any elliptic curve in Weierstrass form.

Let $\phi((x,y)) = (x,-y)$. Let $P_1 = (x_1,y_1)$ and $P_2 = (x_2,y_2)$.

\begin{align*}
\phi(P_1+P_1) &=
\phi \left(
	\left(
		\frac{(3x_1^2+a)^2}{(2y_1)^2}-2x_1,
		\frac{3x_1(3x_1^2+a)}{2y_1}-\frac{(3x_1^2+a)^3}{(2y_1)^3}-y_1
	\right)
\right) \\
&= \left(
	\frac{(3x_1^2+a)^2}{(2y_1)^2}-2x_1,
	\frac{(3x_1^2+a)^3}{(2y_1)^3} - \frac{3x_1(3x_1^2+a)}{2y_1} + y_1
\right)
\end{align*}

\begin{align*}
\phi(P_1)+\phi(P_1) &= (x_1,-y_1) + (x_1,-y_1) \\
&= \left(
	\frac{(3x_1^2+a)^2}{(-2y_1)^2}-2x_1,
	\frac{3x_1(3x_1^2+a)}{-2y_1}-\frac{(3x_1^2+a)^3}{(-2y_1)^3}+y_1
\right) \\
&= \left(
	\frac{(3x_1^2+a)^2}{(2y_1)^2}-2x_1,
	\frac{(3x_1^2+a)^3}{(2y_1)^3} - \frac{3x_1(3x_1^2+a)}{2y_1} + y_1
\right)
\end{align*}

Thus $\phi(P_1 + P_1) = \phi(P_1) + \phi(P_1)$.

\begin{align*}
\phi(P_1+P_2) &= 
\phi \left(
	\left(
		\frac{(y_2-y_1)^2}{(x_2-x_1)^2}-x_1-x_2,
		\frac{(2x_1+x_2)(y_2-y_1)}{(x_2-x_1)}-\frac{(y_2-y_1)^3}{(x_2-x_1)^3}-y_1
	\right)
\right) \\
&= \left(
	\frac{(y_2-y_1)^2}{(x_2-x_1)^2}-x_1-x_2,
	\frac{(y_2-y_1)^3}{(x_2-x_1)^3} - \frac{(2x_1+x_2)(y_2-y_1)}{(x_2-x_1)} + y_1
\right)
\end{align*}

\begin{align*}
\phi(P_1) + \phi(P_2) &= (x_1, -y_1) + (x_2, -y_2) \\
&=
\left(
	\frac{(-y_2+y_1)^2}{(x_2-x_1)^2}-x_1-x_2,
	\frac{(2x_1+x_2)(-y_2+y_1)}{(x_2-x_1)}-\frac{(-y_2+y_1)^3}{(x_2-x_1)^3}+y_1
\right)
\\
&= \left(
	\frac{(y_2-y_1)^2}{(x_2-x_1)^2}-x_1-x_2,
	\frac{(y_2-y_1)^3}{(x_2-x_1)^3} - \frac{(2x_1+x_2)(y_2-y_1)}{(x_2-x_1)} - y_1
\right)
\end{align*}

Thus $\phi(P_1 + P_2) = \phi(P_1) + \phi(P_2)$. We ignore the cases with $\infty$ because they are trivial. Therefore $\phi$ is a homomorphism.

(b) Show that $(x,y) \mapsto (\zeta x, -y)$, where $\zeta$ is a nontrivial cube root of 1, is an automorphism of the elliptic curve $y^2 = x^3 + B$.

Let $\psi((x,y)) = (\zeta x, -y)$. Define $P_1$ and $P_2$ as in (a).

\begin{align*}
\psi(P_1+P_1) &=
\psi \left(
	\left(
		\frac{(3x_1^2)^2}{(2y_1)^2}-2x_1,
		\frac{3x_1(3x_1^2)}{2y_1}-\frac{(3x_1^2)^3}{(2y_1)^3}-y_1
	\right)
\right) \\
&= \left(
	\zeta \left(\frac{(3x_1^2)^2}{(2y_1)^2}-2x_1 \right),
	\frac{(3x_1^2)^3}{(2y_1)^3} - \frac{3x_1(3x_1^2)}{2y_1} + y_1
\right)
\end{align*}

\begin{align*}
\psi(P_1)+\psi(P_1) &= (\zeta x_1,-y_1) + (\zeta x_1,-y_1) \\
&= \left(
	\frac{(3(\zeta x_1)^2)^2}{(-2y_1)^2}-2\zeta x_1,
	\frac{3\zeta x_1(3(\zeta x_1)^2)}{-2y_1}-\frac{(3 (\zeta x_1)^2)^3}{(-2y_1)^3}+y_1
\right) \\
&= \left(
	\zeta \left( \frac{(3x_1^2)^2}{(2y_1)^2}-2x_1 \right),
	\frac{(3x_1^2)^3}{(2y_1)^3} - \frac{3x_1(3x_1^2)}{2y_1} + y_1
\right)
\end{align*}

Thus $\psi(P_1+P_1) = \psi(P_1) + \psi(P_1)$.

\begin{align*}
\psi(P_1+P_2) &= 
\psi \left(
	\left(
		\frac{(y_2-y_1)^2}{(x_2-x_1)^2}-x_1-x_2,
		\frac{(2x_1+x_2)(y_2-y_1)}{(x_2-x_1)}-\frac{(y_2-y_1)^3}{(x_2-x_1)^3}-y_1
	\right)
\right) \\
&= \left(
	\zeta \left(\frac{(y_2-y_1)^2}{(x_2-x_1)^2}-x_1-x_2\right),
	\frac{(y_2-y_1)^3}{(x_2-x_1)^3} - \frac{(2x_1+x_2)(y_2-y_1)}{(x_2-x_1)} + y_1
\right)
\end{align*}

\begin{align*}
\psi(P_1) + \psi(P_2) &= (\zeta x_1, -y_1) + (\zeta x_2, -y_2) \\
&=
\psi\left( 
	\left(
		\frac{(-y_2+y_1)^2}{( x_2 -  x_1)^2}- x_1-  x_2,
		\frac{(2 x_1+ x_2)*(-y_2+y_1)}{(x_2-x_1)}-\frac{(-y_2+y_1)^3}{( x_2- x_1)^3}+y_1
	\right)
\right) \\
&= \left(
	\frac{(y_2-y_1)^2}{(\zeta x_2-\zeta x_1)^2}-\zeta x_1-\zeta x_2,
	\frac{(y_2-y_1)^3}{(\zeta x_2-\zeta x_1)^3} - \frac{(2\zeta x_1+\zeta x_2)(y_2-y_1)}{(\zeta x_2-\zeta x_1)} + y_1
\right)
\\
&=
\left(
	\frac{(y_2-y_1)^2}{\zeta^2(x_2-x_1)^2}-\zeta x_1-\zeta x_2,
	\frac{(y_2-y_1)^3}{\zeta^3(x_2-x_1)^3} - \frac{\zeta(2x_1+x_2)(y_2-y_1)}{\zeta(x_2-x_1)} + y_1
\right) \\
&=
\left(
	\zeta \left( \frac{(y_2-y_1)^2}{(x_2-x_1)^2}-x_1-x_2 \right),
	\frac{(y_2-y_1)^3}{(x_2-x_1)^3} - \frac{(2x_1+x_2)(y_2-y_1)}{(x_2-x_1)} + y_1
\right)
\end{align*}

Thus $\psi(P_1 + P_2) = \psi(P_1) + \psi(P_2)$. Again, we skip $\infty$. Therefore $\psi$ is a homomorphism.

(c) Show that $(x, y) \mapsto (−x, iy)$, is an automorphism of the elliptic curve $y^2 = x^3 + Ax$.

\section{Washington 6.1}
Let E be the curve $y^2 = x^3+1$ over $F_q$, where $q \equiv 2 \mod 3$. By proposition 4.33, $E$ is supersingular. Let $\omega \in F_{q^2}$ be a primitive third root of unity. Note that $\omega \not \in F_q$ since the order of $F_q^\times$ is $q−1$, which is not a multiple of $3$.

Show that the map
$$\beta: E(\bar F_q) \to E(\bar F_q), (x,y) \mapsto (\omega_3 x, y), \beta(\infty) = \infty$$
is an isomorphism.

\end{document}